Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-05-31 measurements.tex
added haec ack

\paragraph{Baseline encoding results} The baseline results involve no recording
of the \ac{DAG} and are performed in a \emph{by-the-book} fashion. The encoder
uses only one thread. And the difference between the non-blocked and blocked
encoding is that in the blocked scheme, the matrix multiplications are performed
dividing the matrices in sub-blocks in order to make the algorithm cache
efficient as described in Section~\ref{sub:implementation-multicore}.

\paragraph{Encoding results} The encoding results were performed using the
method described in Section~\ref{sub:implementation-multicore}. The time
recorded includes the dependencies resolving, creation of the \ac{DAG}, and the
task scheduling. In practice, it would suffice to calculate and store this
information only once per generation size.

\paragraph{Decoding results} The differences between encoding and decoding, is
that the decoding task also involves the matrix inversion. Similarly as with the
encoding results, the time recorded includes the dependencies resolving, the
creation of the \ac{DAG} and the task scheduling. However, to decode, these
calculations are also made for inverting the matrix of coding coefficients.

>>>>

\paragraph{Baseline encoding} The baseline results involve no recording
of the \ac{DAG} and are performed in a \emph{by-the-book} fashion. The encoder
uses only one thread. And the difference between the non-blocked and blocked
encoding is that in the blocked scheme, the matrix multiplications are performed
dividing the matrices in sub-blocks in order to make the algorithm cache
efficient as described in Section~\ref{sub:implementation-multicore}.

\paragraph{Encoding blocked} The encoding results were performed using the
method described in Section~\ref{sub:implementation-multicore}. The time
recorded includes the dependencies resolving, creation of the \ac{DAG}, and the
task scheduling. In practice, it would suffice to calculate and store this
information only once per generation size.

\paragraph{Decoding blocked} The differences between encoding and decoding, is
that the decoding task also involves the matrix inversion. Similarly as with the
encoding results, the time recorded includes the dependencies resolving, the
creation of the \ac{DAG} and the task scheduling. However, to decode, these
calculations are also made for inverting the matrix of coding coefficients.

### 2016-05-31 raspi_journal.tex
added haec ack

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{This research has been financed by the CROSSFIRE MITN Marie
Curie project (317126) from the European Comission FP7 framework,
the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B)
and the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted
by the Danish Council for Independent Research (Det Frie Forskningsr\r{a}d).}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{This research has been financed by the CROSSFIRE MITN Marie
Curie project (317126) from the European Comission FP7 framework,
the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B)
, the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted
by the Danish Council for Independent Research (Det Frie Forskningsr\r{a}d),
and by the German Research Foundation (DFG) within the Collaborative Research Center SFB 912 – HAEC.}
